%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8
% THESIS ACKNOWLEDGEMENTS

% Use the following style if the acknowledgements are long:
%\begin{acknowledgementslong}
%\end{acknowledgmentslong}

\begin{acknowledgements}


I would like to express my deepest gratitude to my supervisor, Prof. Marco Baglietto, for his patience, caring, guiding and mentoring. His guidance helped me since the beginning of this work. I also would like to thank him for the enormous patience he had and the dose of sarcasm added o each conversation. 

I would like to thank my second supervisor, Prof. Fulvio Mastrogiovanni, for his big help, huge encouragement and for always bringing a good laugh among us. 

I would like to express my gratitude to my co-supervisor Tommaso Falchi Delitalia, who helped me so much especially in the beginning of the work. He is the one who made this thesis possible and moreover, the one who let me discover the wonderful world of aerial robotics.

I would like to express my deepest gratitude to the entire EMARO staff, to the professors who supported me and thought many interest things. Special thanks to Gaetan Garcia, the funny man who thought me robotics. 

Sincere gratitude to my colleagues and friends who gave me always the support needed. In particular Alessio Capitanelli who started a beautiful journey with me five years ago. Thanks to my lab fellow Luca Buoncompagni who helped me in many ways in the most difficult moments.

I express my gratitude to my girlfriend Laura, who begun this adventure with me two years ago and continuously supports me.
 
Finally, I take this opportunity to express the profound gratitude from my deep heart to my beloved parents, for the enormous support they gave me since the beginning of my life.

Any future success that I may accomplish will be caused by those mentioned above, thank you.
  


\end{acknowledgements}